The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2024-02-09 src/paper/theory.tex
First sketch of proof for second part of lemma 2

\begin{proof}[Proof of \cref{lem:many_sided_manifold}]
    Just like in the proof of \cref{prop:many_sided_general}, the random order value can be expressed as follows:
    \begin{align*}
        \varphi_P^n &= \E[f(X_n)].
    \end{align*}
    Furthermore, as $f$ is continuous and bounded on $[0, 1]^L$, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
    Therefore,
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
        &= \E[f(X)] \\
        &= \E[f(a_1(\xi), \dots, a_L(\xi))] \\
        &= \int_0^1 f(a_1(s), \dots a_L(s)) \mathrm{d}H(s).
    \end{align*}
\end{proof}

>>>>

\begin{proof}[Proof of \cref{lem:many_sided_manifold}]
    Just like in the proof of \cref{prop:many_sided_general}, the random order value can be expressed as follows:
    \begin{align*}
        \varphi_P^n &= \E[f(X_n)].
    \end{align*}
    Furthermore, as $f$ is continuous and bounded on $[0, 1]^L$, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
    Therefore,
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
        &= \E[f(X)] \\
        &= \E[f(a_1(\xi), \dots, a_L(\xi))] \\
        &= \int_0^1 f(a_1(s), \dots a_L(s)) \mathrm{d}H(s).
    \end{align*}

    For the fringe value, the proof is similar, with a couple of additional steps.
    First, fix some fringe player $A_{li}$.
    Let $Y_n$ be the random variable describing the share of each type of fringe player that precede player $A_{li}$.
    Also, let $Q_n$ be the random variable describing whether player $P$ precedes player $A_{li}$.
    Then, the value of fringe player $A_{li}$ is
    \begin{align*}
        \varphi_{A_{li}}^n &= \E[ \mathbf{1}[Q_n = 1] (f(Y_1, \dots, Y_l + 1/n, \dots, Y_L) - f(Y_1, \dots, Y_l, \dots, Y_L)) ],
    \end{align*}
    and the value of the whole fringe of type $A_l$ is
    \begin{align*}
        \varphi_{A_{l}}^n = n \varphi_{A_{li}}^n = \E \bigg[ \underbrace{\mathbf{1}[Q_n = 1] \frac{f(Y_1, \dots, Y_l + 1/n, \dots, Y_L) - f(Y_1, \dots, Y_l, \dots, Y_L)}{1/n}}_{\coloneqq \Delta_n} \bigg].
    \end{align*}

    Now notice that, because the number of fringe players goes to infinity,
    \begin{align*}
        X_n \xrightarrow[]{d} (a_1(\xi), \dots, a_L(\xi)) &\implies Y_n \xrightarrow[]{d} (a_1(\xi), \dots, a_L(\xi)) \\
        &\implies (Y_1, \dots, Y_n) | Y_l = a_l(s) \xrightarrow[]{d} (a_1(s), \dots, a_l(s)) .
    \end{align*}
    Furthermore,
    \begin{align*}
        \Pr(Q_n = 1 | [Y_n]_l = a_l(s)) \to H(s).
    \end{align*}
    Finally, for fixed $(Y_1, \dots, Y_L)$,
    \begin{align*}
        \Delta_n \to \partial_l f(Y_1, \dots, Y_l, \dots, Y_L).
    \end{align*}

    Putting it all together,
    \begin{align*}
        \lim_{n \to \infty} \varphi_{A_{l}}^n &= \lim_{n \to \infty} \E[\Delta_n (Y_n)] \\
        &= \E[ H(s) \partial_l f(Y_1, \dots, Y_L) ] \\
        &= \int_0^1 H(s) \partial_l f(a_1(s), \dots, a_L(s)) \mathrm{d} a_l(s) \\
        &= \int_0^1 H(s) a_l'(s) \partial_l f(a_1(s), \dots, a_L(s)) \ds.
    \end{align*}
